Using Genetic Algorithms to Optimize the Analogue Method for Precipitation forecasting in the Swiss Alps

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
Rewriting the abstract.

\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting. This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure. This sequential calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared. In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies. Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before. 
	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now. Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
	These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
	}

@@

The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window. However, it doesn't provide an objective selection of the pressure level and temporal window. The only option is to try systematically every combination, which may be acceptable for no more than 2 levels. However, \citet{Horton2012a} showed that additional pressure levels may improve the method.

@@

When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?} ''. And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''. \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions. \citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.

>>>>

\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting. This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure. This sequential calibration has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
In order to surpass these limitations, a global optimization technique was assessed, namely genetic algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies. Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
}

@@

The sequential calibration is fast to optimize one spatial window for a given pressure level and temporal window. However, it doesn't provide an objective selection of the pressure level and temporal window. The only option is to try systematically every combination, which may be acceptable for no more than 2 levels. However, \citet{Horton2012a} showed that additional pressure levels may improve the method.

@@

When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?} ''. And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''. \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions. \citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.

### 2015-11-18 Optimization case study - Journal of Hydrology/template.tex
Rewriting the abstract.

\abstract{
We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy. The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}
\begin{document}

>>>>

\abstract{

	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now. Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).

We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy. The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}
\begin{document}
